---
title: "minecraft_analysis_supplemental"
author: "Valentin"
date: "`r Sys.Date()`"
output: html_document
encoding: UTF-8
---

```{r, SETTINGS-knitr, include=FALSE}
stopifnot(require(knitr))
options(width = 90)
opts_chunk$set(
  cache = FALSE,
  comment = NA,
  message = FALSE,
  warning = FALSE
)
```







# import libraries
```{r, echo=FALSE, include=FALSE}

# load libraries

                    
library(foreign)  
library(plyr)

library(lme4)
library(car)
library(TOSTER)

library(ggplot2)          
library(tidyverse)
library(sjPlot)
library(ggpubr)
library(Hmisc)

library(jtools)
library(nlme)
library(rcompanion)

library(brms)
library(ggbeeswarm)
library(psych)
library(psycho)

library(haven)

library(sjstats)
library(bayestestR)
library(see)

library(afex)

```
<br>


# create the dataset

#### read input
```{r, echo=FALSE}


minecraft_data = read.spss('minecraft_data.sav', use.value.labels = TRUE, to.data.frame = TRUE)


```



#### compute additional variables
```{r, echo=FALSE}

# compute recall difference as an additional variable
minecraft_data$memory_difference = minecraft_data$LTM -  minecraft_data$STM

# compute memory quotient as an additional variable
minecraft_data$memory_quotient =  minecraft_data$LTM / minecraft_data$STM
minecraft_data$retention_score = minecraft_data$memory_quotient * 100

```



#### z transform control variables for the extended analysis models
```{r, echo=FALSE}

minecraft_data$binNumDayTwo_Ztrans = scale(minecraft_data$binNumDayTwo)
minecraft_data$IPQ_Ztrans = scale(minecraft_data$IPQ)

```


#### relevel "diagnosis"
```{r, echo=FALSE}

minecraft_data$diagnosis = factor(minecraft_data$diagnosis, levels = c( "ADHD","control"))

```



#### exclude participants

- subject 11 was non-compliant during experiment
- subject 39 did not show up after inital diagnostic session
- subjects 40 and 57: technical issues


```{r, echo=FALSE}

# exclude participants
minecraft_data = subset(minecraft_data, subject != 11 & subject != 39 & subject != 40 & subject != 57)

```




#### get data into long format (by time)
```{r, echo=FALSE}

# all data
minecraft_data_long = gather(minecraft_data, key = "time", value = "words_remembered", STM,LTM)
minecraft_data_long$time = as.factor(minecraft_data_long$time)


```
<br>





#### generate a dataset with exploration variables in long format
```{r, echo = FALSE}

# transform to long data format (by day)
    
# for time
minecraft_position_long_time = gather(minecraft_data, key = "day", value = "time_spent", totalTimeDayOne, totalTimeDayTwo)

# for distance
minecraft_position_long_distance = gather(minecraft_data, key = "day", value = "distance_travelled", distanceDayOne, distanceDayTwo)

# for VE
minecraft_position_long_VE = gather(minecraft_data, key = "day", value = "VE_type", VE_day1, VE_day2)

# for normalized entropy (entries)
minecraft_position_long_binEntropyEntries_norm = gather(minecraft_data, key = "day", value = "binEntropyEntriesNormalized", binEntropyEntriesDayOneNormalized, binEntropyEntriesDayTwoNormalized)

# for binNum
minecraft_position_long_binNum = gather(minecraft_data, key = "day", value = "binNum", binNumDayOne, binNumDayTwo)

# for normalized binNum
minecraft_position_long_binNum_norm = gather(minecraft_data, key = "day", value = "binNumNormalized", binNumDayOneNormalized, binNumDayTwoNormalized)


# merge all long datasets into one
minecraft_position_long = minecraft_position_long_time 
minecraft_position_long$distance_travelled = minecraft_position_long_distance$distance_travelled
minecraft_position_long$VE_type = minecraft_position_long_VE$VE_type
minecraft_position_long$binEntropyEntriesNormalized = minecraft_position_long_binEntropyEntries_norm$binEntropyEntriesNormalized
minecraft_position_long$binNum = minecraft_position_long_binNum$binNum 
minecraft_position_long$binNumNormalized = minecraft_position_long_binNum_norm$binNumNormalized 

# factorize and rename levels of "day"
minecraft_position_long$day = as.factor(minecraft_position_long$day)
levels(minecraft_position_long$day) = c("one", "two")

# remove redundant dataframes
remove(minecraft_position_long_VE, minecraft_position_long_distance, minecraft_position_long_time, minecraft_position_long_binEntropyEntries_norm, minecraft_position_long_binNum, minecraft_position_long_binNum_norm)



```



#### add functions
```{r, echo=FALSE}

ROPE_bySD = function(posterior_distribution){

  range_myROPE =  c( -0.1*sd(posterior_distribution), 0.1*sd(posterior_distribution) )
  return(range_myROPE)
}


```




#### set brms theme
```{r, echo=FALSE}

theme_set(theme_default())

```
<br>







#####################################################################################################################
# Compare environment types

#### Comparability of environments (immersion/IPQ)
```{r, echo=FALSE}


# exploration time
t.test(totalTimeDayOne~VE_day1, data = minecraft_data) 


# binNum
t.test(binNumDayOne~VE_day1, data = minecraft_data) 


# immersion
t.test(IPQ~VE_day2, data = minecraft_data) 

```



#### does the type of VE infleunce retention?

```{r, echo=FALSE}

t.test(retention_score~VE_day2, data = minecraft_data) 

```







#####################################################################################################################
# Analysis of recognition data
<br>


## ANOVA for corrected hitrate (sanity check to see that frequentist measures give the same results)

```{r, echo=FALSE}

# change contrasts so r gives the same results as SPSS (SPSS uses sum instead of treatment contrast)
options(contrasts = c("contr.sum", "contr.poly"))
#options(contrasts = c("contr.treatment", "contr.poly"))

Anova(lm(CorrectedHitrate ~ diagnosis*novelty, data = minecraft_data), type = 3)

ggplot(minecraft_data, aes(x = diagnosis, y = CorrectedHitrate, group = novelty, colour = novelty)) + 
      stat_summary(fun.data = "mean_cl_boot", position=position_dodge(width = 0.1), colour = "black") + 
      stat_summary(fun.y = mean, geom = "line", position=position_dodge(width = 0.1)) +
      geom_beeswarm(dodge.width=0.2) +
      scale_color_discrete(name = "novelty", labels = c("familiar", "novel")) +
      scale_x_discrete(labels = c("ADHD", "TD")) # change x axis tick labels

      

```




```{r, echo=FALSE}


# recognition (barplots)
p_recognition = ggplot(minecraft_data, aes(x = splitter_groups, y = CorrectedHitrate)) + 
    theme_bw() +
    stat_summary(fun = "mean", geom = "bar", alpha = 0.3, width = 0.5, fill = "royalblue") +
    geom_beeswarm(colour = rgb(0,45,92, maxColorValue = 255), cex = 1.4, size = 1.3) +
    stat_summary(fun.data = "mean_cl_boot", geom="errorbar", width = .4, colour = rgb(0,45,92, maxColorValue = 255)) + 
    scale_y_continuous(expand = c(0,0), limits = c(0,1.1)) + # force x axis to start at y axis 0
    ylab("accuracy") + # change y axis label
    xlab("") + # hide x axis label
    scale_x_discrete(labels = c("ADHD-familiar", "ADHD-novel", "TD-familiar", "TD-novel")) + # change x axis tick labels
    theme(panel.border = element_blank(), axis.line = element_line(colour = "black"))

p_recognition

#ggsave(file="recognition.svg", plot=p_recognition, width = 190, units = "mm")



```




```{r, echo=FALSE}

#### load the model reported in the paper
minecraft_recognition_full = readRDS(file = "minecraft_recognition_full.rds")


#### uncomment the following to fit a new model

# # 
# # # set priors
# # prior_intercept = set_prior("student_t(3,0.7,0.2)", class = "Intercept")
# # prior_sigma = set_prior("student_t(3,0,0.3)", class = "sigma")
# # 
# # control_novel is reference category
# minecraft_recognition_full <- brm(
#     CorrectedHitrate ~ diagnosis*novelty,
#     data = minecraft_data,
#     #prior = c(prior_intercept, prior_sigma),
#     sample_prior = TRUE,
#     chains = 4, cores = 4,
#     save_all_pars= TRUE
# )
# 
# #remove(prior_intercept, prior_sigma)
# 
# 
# saveRDS(minecraft_recognition_full, file = "minecraft_recognition_full.rds")

```



```{r, echo=FALSE}

summary(minecraft_recognition_full)
plot(minecraft_recognition_full, ask = FALSE)
plot(conditional_effects(minecraft_recognition_full), ask = FALSE)
pp_check(minecraft_recognition_full)

```





#### get the posterior distribution of the differences between groups


```{r, echo=FALSE}

# extract the posterior distribution for the reference group (adhd_familiar)
posterior_adhd_familiar = posterior_samples(minecraft_recognition_full, pars = "b_Intercept")$b_Intercept

# extract postrerior distributions of model effects
posterior_effect_novelty = posterior_samples(minecraft_recognition_full, pars = "b_noveltynovel")$b_noveltynovel
posterior_effect_diagnosis = posterior_samples(minecraft_recognition_full, pars = "b_diagnosiscontrol")$b_diagnosiscontrol
posterior_effect_interaction = posterior_samples(minecraft_recognition_full, pars = "b_diagnosiscontrol:noveltynovel")$`b_diagnosiscontrol:noveltynovel`



# compute posterior distributions for the other groups by combining intercept and model effects
posterior_adhd_novel = posterior_adhd_familiar + posterior_effect_novelty
posterior_control_familiar = posterior_adhd_familiar + posterior_effect_diagnosis
posterior_control_novel = posterior_adhd_familiar + posterior_effect_novelty + posterior_effect_diagnosis + posterior_effect_interaction

# compute all group differences
posterior_diff_adhd_novel_adhd_familiar = posterior_adhd_novel - posterior_adhd_familiar
posterior_diff_adhd_familiar_control_familiar = posterior_adhd_familiar - posterior_control_familiar
posterior_diff_adhd_familiar_control_novel = posterior_adhd_familiar - posterior_control_novel
posterior_diff_adhd_novel_control_novel = posterior_adhd_novel - posterior_control_novel
posterior_diff_adhd_novel_control_familiar = posterior_adhd_novel - posterior_control_familiar
posterior_diff_control_novel_control_familiar =  posterior_control_novel - posterior_control_familiar

# compute main effects of diagnosis and novelty
posterior_main_effect_diagnosis = posterior_adhd_familiar + posterior_adhd_novel - posterior_control_familiar - posterior_control_novel
posterior_main_effect_novelty = posterior_adhd_familiar + posterior_control_familiar - posterior_adhd_novel - posterior_control_novel


```







```{r, echo=FALSE}

#### set ROPE

# manually define the ROPE to use for the posterior differences, since otherwise the range defaults to [-0.1, 0.1]
# alternatively, the ROPE may also be estimated through the standard deviation of each individual distribution [-0.1 * SD, 0.1 * SD]
# as only a difference of > 5% is meaningful, this is used as the ROPE for this analysis
rope_minecraft_recognition_full = c(-0.05,0.05) # equals a minimal difference of 5% in corrected hitrate


CI_rope = 1 # ROPE_percentage refers to all of the posterior distribution (100%)
#CI_rope = .95 # ROPE_percentage refers to the HDI (95%)



#### plot posterior distributions of the group differences and report HDI and percentage in ROPE

# control familiar vs. control novel
ROPE = rope(posterior_diff_control_novel_control_familiar, ci = .95, range(rope_minecraft_recognition_full))
p_diff_control_novel_control_familiar = plot(ROPE) +
  geom_vline(xintercept=mean(posterior_diff_control_novel_control_familiar)) +
  ggtitle("TD_novel minus TD_familiar") +
#  scale_x_continuous(expand = c(0,0), limits = c(-30,20), breaks = c(-20, -10, 0, 10)) + # force y axis to start at x axis 0
   #xlim(c(-30, 20)) +
   scale_y_continuous(expand = c(0,0), limits = c(0,1.1)) + # force x axis to start at y axis 0
  xlab(label = "difference in recognition") +
  ylab(label = "posterior probability") +
  theme( axis.text.y = element_blank(), 
         axis.ticks.y = element_blank(), 
         axis.text.x = element_text(size = 10, family = "sans"), 
         axis.title.x = element_text(size=10, family = "sans"), 
         axis.title.y = element_text(size=10, family = "sans"), 
         title = element_text(size=10, family = "sans")) +
  guides(fill = FALSE)
  
p_diff_control_novel_control_familiar

describe_posterior(posterior_diff_control_novel_control_familiar, centrality = "mean", ci = .95, rope_ci = CI_rope, rope_range = rope_minecraft_recognition_full)
#ggsave("posterior_diff_control_novel_control_familiar.svg", p_diff_control_novel_control_familiar, height = 85, width = 105, units = "mm")


# adhd familiar vs. adhd novel
ROPE = rope(posterior_diff_adhd_novel_adhd_familiar, ci = .95, range(rope_minecraft_recognition_full))
p_posterior_diff_adhd_novel_adhd_familiar = plot(ROPE) +
  geom_vline(xintercept=mean(posterior_diff_adhd_novel_adhd_familiar)) +
  ggtitle("ADHD_novel minus ADHD_familiar") +
   scale_y_continuous(expand = c(0,0), limits = c(0,1.1)) + # force x axis to start at y axis 0
  xlab(label = "difference in recognition") +
  ylab(label = "posterior probability") +
  theme( axis.text.y = element_blank(), 
         axis.ticks.y = element_blank(), 
         axis.text.x = element_text(size = 10, family = "sans"), 
         axis.title.x = element_text(size=10, family = "sans"), 
         axis.title.y = element_text(size=10, family = "sans"), 
         title = element_text(size=10, family = "sans")) +
  guides(fill = FALSE)

p_posterior_diff_adhd_novel_adhd_familiar

describe_posterior(posterior_diff_adhd_novel_adhd_familiar, centrality = "mean", ci = .95, rope_ci = CI_rope, rope_range = rope_minecraft_recognition_full)
#ggsave("posterior_diff_adhd_novel_adhd_familiar.svg", p_posterior_diff_adhd_novel_adhd_familiar, height = 85, width = 105, units = "mm")


# adhd novel vs. control novel
ROPE = rope(posterior_diff_adhd_novel_control_novel, ci = .95, range(rope_minecraft_recognition_full))
p_posterior_diff_adhd_novel_control_novel = plot(ROPE) +
  geom_vline(xintercept=mean(posterior_diff_adhd_novel_control_novel)) +
  ggtitle("ADHD_novel minus TD_novel") +
  scale_y_continuous(expand = c(0,0), limits = c(0,1.1)) + # force x axis to start at y axis 0
  xlab(label = "difference in recognition") +
  ylab(label = "posterior probability") +
  theme( axis.text.y = element_blank(), 
         axis.ticks.y = element_blank(), 
         axis.text.x = element_text(size = 10, family = "sans"), 
         axis.title.x = element_text(size=10, family = "sans"), 
         axis.title.y = element_text(size=10, family = "sans"), 
         title = element_text(size=10, family = "sans")) +
  guides(fill = FALSE)

p_posterior_diff_adhd_novel_control_novel

describe_posterior(posterior_diff_adhd_novel_control_novel, centrality = "mean", ci = .95, rope_ci = CI_rope, rope_range = rope_minecraft_recognition_full)
#ggsave("posterior_diff_adhd_novel_control_novel.svg", p_posterior_diff_adhd_novel_control_novel, height = 85, width = 105, units = "mm")



# adhd familiar vs. control familiar
ROPE = rope(posterior_diff_adhd_familiar_control_familiar, ci = .95, range(rope_minecraft_recognition_full))
p_posterior_diff_adhd_familiar_control_familiar = plot(ROPE) +
  geom_vline(xintercept=mean(posterior_diff_adhd_familiar_control_familiar)) +
  ggtitle("ADHD_familiar minus TD_familiar") +
  scale_y_continuous(expand = c(0,0), limits = c(0,1.1)) + # force x axis to start at y axis 0
  xlab(label = "difference in recognition") +
  ylab(label = "posterior probability") +
  theme( axis.text.y = element_blank(), 
         axis.ticks.y = element_blank(), 
         axis.text.x = element_text(size = 10, family = "sans"), 
         axis.title.x = element_text(size=10, family = "sans"), 
         axis.title.y = element_text(size=10, family = "sans"), 
         title = element_text(size=10, family = "sans")) +
  guides(fill = FALSE)

p_posterior_diff_adhd_familiar_control_familiar

describe_posterior(posterior_diff_adhd_familiar_control_familiar, centrality = "mean", ci = .95, rope_ci = CI_rope, rope_range = rope_minecraft_recognition_full)
#ggsave("posterior_diff_adhd_familiar_control_familiar.svg", p_posterior_diff_adhd_familiar_control_familiar, height = 85, width = 105, units = "mm")



```




#### main effects of diagnosis and novelty

```{r, echo=FALSE}


# manually define the ROPE to use for the posterior differences, since otherwise the range defaults to [-0.1, 0.1]
# alternatively, the ROPE may also be estimated through the standard deviation of each individual distribution [-0.1 * SD, 0.1 * SD]
# as only a difference of > 0.05% is meaningful, this is used as the ROPE for this analysis
rope_minecraft_recognition_full = c(-0.05, 0.05) # equals a minimal difference of 5% in corrected hitrate

CI_rope = 1 # ROPE_percentage refers to all of the posterior distribution (100%)
#CI_rope = .95 # ROPE_percentage refers to the HDI (95%)




# main effect diagnosis
ROPE = rope(posterior_main_effect_diagnosis, ci = .95, range(rope_minecraft_recognition_full))
p_posterior_main_effect_diagnosis = plot(ROPE) +
  geom_vline(xintercept=mean(posterior_main_effect_diagnosis)) +
  ggtitle("main effect diagnosis") +
  scale_y_continuous(expand = c(0,0), limits = c(0,1.1)) + # force x axis to start at y axis 0
  xlab(label = "difference in recognition") +
  ylab(label = "posterior probability") +
  theme( axis.text.y = element_blank(), 
         axis.ticks.y = element_blank(), 
         axis.text.x = element_text(size = 10, family = "sans"), 
         axis.title.x = element_text(size=10, family = "sans"), 
         axis.title.y = element_text(size=10, family = "sans"), 
         title = element_text(size=10, family = "sans")) +
  guides(fill = FALSE)

p_posterior_main_effect_diagnosis

describe_posterior(posterior_main_effect_diagnosis, centrality = "mean", ci = .95, rope_ci = CI_rope, rope_range = rope_minecraft_recognition_full)
#ggsave("posterior_main_effect_diagnosis.svg", p_posterior_main_effect_diagnosis, height = 85, width = 105, units = "mm")






# main effect of novelty
ROPE = rope(posterior_main_effect_novelty, ci = .95, range(rope_minecraft_recognition_full))
p_posterior_main_effect_novelty = plot(ROPE) +
  geom_vline(xintercept=mean(posterior_main_effect_novelty)) +
  ggtitle("main effect novelty") +
  scale_y_continuous(expand = c(0,0), limits = c(0,1.1)) + # force x axis to start at y axis 0
  xlab(label = "difference in recognition") +
  ylab(label = "posterior probability") +
  theme( axis.text.y = element_blank(), 
         axis.ticks.y = element_blank(), 
         axis.text.x = element_text(size = 10, family = "sans"), 
         axis.title.x = element_text(size=10, family = "sans"), 
         axis.title.y = element_text(size=10, family = "sans"), 
         title = element_text(size=10, family = "sans")) +
  guides(fill = FALSE)

p_posterior_main_effect_novelty

describe_posterior(posterior_main_effect_novelty, centrality = "mean", ci = .95, rope_ci = CI_rope, rope_range = rope_minecraft_recognition_full)
#ggsave("posterior_main_effect_novelty.svg", p_posterior_main_effect_novelty, height = 85, width = 105, units = "mm")





```



