---
title: "minecraft_analysis_descriptives"
author: "Valentin"
date: "`r Sys.Date()`"
output: html_document
encoding: UTF-8
---

```{r, SETTINGS-knitr, include=FALSE}
stopifnot(require(knitr))
options(width = 90)
opts_chunk$set(
  cache = FALSE,
  comment = NA,
  message = FALSE,
  results = "asis",
  warning = FALSE
)
```







# import libraries
```{r, echo=FALSE}

# load libraries
library(foreign) 
library(Hmisc)
library(tidyverse)
library(summarytools)


```
<br>


# read input
```{r, echo=FALSE}

minecraft_data = read.spss('minecraft_data.sav', use.value.labels = TRUE, to.data.frame = TRUE)


```




#### compute additional variables
```{r, echo=FALSE}

# compute recall difference as an additional variable
minecraft_data$memory_difference = minecraft_data$LTM -  minecraft_data$STM

# compute memory quotient as an additional variable
minecraft_data$memory_quotient =  minecraft_data$LTM / minecraft_data$STM
minecraft_data$retention_score = minecraft_data$memory_quotient * 100

```



#### z transform control variables for the extended analysis models
```{r, echo=FALSE}

minecraft_data$binNumDayTwo_Ztrans = scale(minecraft_data$binNumDayTwo)
minecraft_data$IPQ_Ztrans = scale(minecraft_data$IPQ)
minecraft_data$JTCI_Expl_Ztrans = scale(minecraft_data$JTCI_Expl)

```


#### relevel "diagnosis"
```{r, echo=FALSE}

minecraft_data$diagnosis = factor(minecraft_data$diagnosis, levels = c( "ADHD","control"))

```



#### exclude participants

- subject 11 was non-compliant during experiment
- subject 39 did not show up after inital diagnostic session
- subjects 40 and 57: technical issues


```{r, echo=FALSE}

# exclude participants
minecraft_data = subset(minecraft_data, subject != 11 & subject != 39 & subject != 40 & subject != 57)

```



# select variables of interest
```{r, echo=FALSE}

#minecraft_data = select(minecraft_data, subject, Hits, FalseAlarms, CorrectedHitrate, splitter_groups)

```


#### compute subsets
```{r, echo=FALSE}

# subset the single groups
data_control_familiar = minecraft_data[which(minecraft_data$splitter_groups == "control_familiar"), ] 
data_control_novel = minecraft_data[which(minecraft_data$splitter_groups == "control_novel"), ] 
data_adhd_familiar = minecraft_data[which(minecraft_data$splitter_groups == "ADHD_familiar"), ] 
data_adhd_novel = minecraft_data[which(minecraft_data$splitter_groups == "ADHD_novel"), ] 


```
<br>




# sample description

#### script needs to be knit to be displayed properly ####


# total sample
```{r, echo = FALSE}


#dfSummary(minecraft_data, plain.ascii = FALSE, style = "grid", round.digits = 3, graph.magnif = 0.75, valid.col = FALSE, tmp.img.dir = "/tmp")


```


# adhd familiar
```{r, echo = FALSE}

dfSummary(data_adhd_familiar, plain.ascii = FALSE, style = "grid", round.digits = 3, graph.magnif = 0.75, valid.col = FALSE, tmp.img.dir = "/tmp")

```


# adhd novel
```{r, echo = FALSE}

dfSummary(data_adhd_novel, plain.ascii = FALSE, style = "grid", round.digits = 3, graph.magnif = 0.75, valid.col = FALSE, tmp.img.dir = "/tmp")

```


# control familiar
```{r, echo = FALSE}

dfSummary(data_control_familiar, plain.ascii = FALSE, style = "grid", round.digits = 3, graph.magnif = 0.75, valid.col = FALSE, tmp.img.dir = "/tmp")

```


# control novel
```{r, echo = FALSE}

dfSummary(data_control_novel, plain.ascii = FALSE, style = "grid", round.digits = 3, graph.magnif = 0.75, valid.col = FALSE, tmp.img.dir = "/tmp")

```


